---
title: "Whole Genome Sequencing Cost-Benefit Report"
author: WGS Econ Benefit web app
subject: Whole Genome Sequencing
output:
  word_document:
    number_sections: true
    reference_docx: "common/word-styling.docx"
params:
  lab_name: ""
  report_date: ""
  sequencer: ""
  pathogen: ""
  num_isolates: 0
  equip_capital_f: ""
  equip_maint_f: ""
  equip_use_rate_f: ""
  consumables_cost_f: ""
  failure_rate_f: ""
  tech_time_f: ""
  prof_time_f: ""
  overhead_pct_f: ""
  other_costs_f: ""
  glob_technician_pay_f: ""
  glob_professional_pay_f: ""
  equip_per_sample_f: ""
  consumables_per_sample_f: ""
  staff_costs_f: ""
  total_staff_time_f: ""
  other_per_sample_f: ""
  total_cost_per_sample_f: ""
  annual_cost_f: ""
  cases_prevented_f: ""
  illness_cost_avoided_f: ""
  savings_per_dollar_f: ""
---

<!-- https://bookdown.org/yihui/rmarkdown/word-document.html -->
<!-- https://rmarkdown.rstudio.com/articles_docx.html -->

```{r setup, include=FALSE}
library(knitr)
library(magrittr)
library(flextable)
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

# Identifying Information

Laboratory: `r params$lab_name`

Report Date: `r params$report_date`

Sequencer (Make/Model): `r params$sequencer`

# Sample Data

Pathogen of Interest: `r params$pathogen`

Unique Isolates Sequenced (last 12 months): `r params$num_isolates`

# Inputs & Assumptions

## Cost Inputs

```{r}
inputs_tbl <- data.frame(
  category = c(
    "Equipment capital (annualized)",
    "Equipment maintenance (annual)",
    "Equipment use rate (%)",
    "Consumables (annual)",
    "Analytical failure rate (%)",
    "Technician time (minutes/sample)",
    "Professional time (minutes/sample)",
    "Overhead (% of pre-tax wages)",
    "Other costs (annualized)"
  ),
  value = c(
    params$equip_capital_f,
    params$equip_maint_f,
    params$equip_use_rate_f,
    params$consumables_cost_f,
    params$failure_rate_f,
    params$tech_time_f,
    params$prof_time_f,
    params$overhead_pct_f,
    params$other_costs_f
  )
)
colnames(inputs_tbl) <- c("Category", "Value")
flextable(inputs_tbl) %>%
  autofit() %>%
  set_caption(
    as_paragraph(
      as_chunk(
        "User-reported Values",
        props = fp_text_default(font.family = "Arial")
      )
    )
  ) %>%
  set_table_properties(
    opts_word = list(split = FALSE, keep_with_next = TRUE),
    word_title = "Values entered by the user",  #alt text
    word_description = paste(  #alt text
      "Table showing the values reported by the user.",
      "The first column shows the category.",
      "The second column shows the value."
    )
  ) %>%
  font(fontname = "Arial", part = "all") %>%
  align(j = 2, align = "right", part = "all")
```

## Pay Rates

```{r}
pay_tbl <- data.frame(
  role = c("Technician","Professional"),
  rate = c(params$glob_technician_pay_f, params$glob_professional_pay_f)
)
colnames(pay_tbl) <- c("Role", "Fully loaded pay rate")
flextable(pay_tbl) %>%
  autofit() %>%
  set_caption(
    as_paragraph(
      as_chunk(
        "Hourly Pay Rates",
        props = fp_text_default(font.family = "Arial")
      )
    )
  ) %>%
  set_table_properties(
    opts_word = list(split = FALSE, keep_with_next = TRUE),
    word_title = "Pay rates for technicians and professionals",  #alt text
    word_description = paste(  #alt text
      "Table showing the pay rates for technicians and professionals.",
      "The first column shows the employee role.",
      "The second column shows the hourly pay rate."
    )
  ) %>%
  font(fontname = "Arial", part = "all") %>%
  align(j = 2, align = "right", part = "all")
```

# Results

## Per-Sample Costs

```{r}
per_sample_tbl <- data.frame(
  source = c(
    "Equipment",
    "Consumables",
    "Staff (including overhead)",
    "Other"
  ),
  cost = c(
    params$equip_per_sample_f,
    params$consumables_per_sample_f,
    params$staff_costs_f,
    params$other_per_sample_f
  )
)
colnames(per_sample_tbl) <- c("Source", "Cost")
flextable(per_sample_tbl) %>%
  autofit() %>%
  add_footer_row(
    top = FALSE,
    values = list(
      Source = "TOTAL",
      Cost = params$total_cost_per_sample_f
    ),
    colwidths = c(1, 1)
  ) %>%
  set_caption(
    as_paragraph(
      as_chunk(
        "Calculated Cost Per Sample",
        props = fp_text_default(font.family = "Arial")
      )
    )
  ) %>%
  set_table_properties(
    opts_word = list(split = FALSE, keep_with_next = TRUE),
    word_title = "Calculated cost per sample",  #alt text
    word_description = paste(  #alt text
      "Table showing the cost per sample.",
      "The first column shows the source of the cost.",
      "The second column shows the amount."
    )
  ) %>%
  font(fontname = "Arial", part = "all") %>%
  align(j = 2, align = "right", part = "all")
```

## Staff Time

Hands-on staff time per sample: `r params$total_staff_time_f` hours

## Annual Totals

Annual cost for `r params$pathogen` samples: **`r params$annual_cost_f`**

# Cost-Benefit Summary

Estimated cases prevented (last 12 months): **`r params$cases_prevented_f`**

Estimated illness costs avoided:  **`r params$illness_cost_avoided_f`**

Savings per $1 spent: **`r params$savings_per_dollar_f`**


> **Note:** Values use the pathogen's average *cases prevented per 1,000 isolates*
and *cost per case*, applied to your isolate count and the cost structure
captured above.
